<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{b) Built-in Choropleths}
-->

Built-in Choropleths
========================================================

`choroplethr` ships with four built-in choropleths

### US State Choropleths

To create a state level choropleth with your own data you need to call `?state_choropleth` with a data.frame. 

```{r}
    library(choroplethr)
    data(df_pop_state)

    state_choropleth(df_pop_state, 
                     title="2012 State Population Estimates",
                     legend_name="Population")
```

The data.frame must have two columns: one named _region_ and one named _value_. Region must be lower-case state names. Mention specifics of region. Mention `state.names`.

### US County Choropleths

To create a state level choropleth with your own data you need to call `?state_choropleth` with a data.frame. 

```{r}
    library(choroplethr)
    data(df_pop_county)

    county_choropleth(df_pop_county, 
                     title="2012 County Population Estimates",
                     legend_name="Population")
```

The data.frame must have two columns: one named _region_ and one named _value_. Mention specifics of region. Mention `county.names`.


### US ZIP Maps

...
```{r}
    library(choroplethr)
    data(df_pop_zip)

    zip_map(df_pop_zip, 
           title="2012 ZIP Population Estimates",
           legend_name="Population")
```

The data.frame must have two columns: one named _region_ and one named _value_. Mention specifics of region. 

### Country Choropleths (World Map)

```{r}
    library(choroplethr)
    data(df_pop_country)

    zip_map(df_pop_zip, 
           title="2012 Country Population Estimates from the World Bank",
           legend_name="Population")
```
