<!--
  %\VignetteEngine{knitr}
%\VignetteIndexEntry{b) Choosing a Level of Detail (lod)}
-->

Choosing a Level of Detail (lod)
========================================================

The main function in the choroplethr package is called `choroplethr` (`?choroplethr`). It has two required parameters: 
  1. `df` A data.frame which contains one column named `region` and one column named `value`.  df can have other columns, too - but choroplethr only cares about these columns.  
  2. `lod` A string which says the geographic level of detail of the data.  Must be either `state`, `county` or `zip`.
 
As the following example shows, the choice of level of detail is important.
  
## State lod

choroplethr comes with a dataset, `df_pop_state`, which contains 2012 population estimates for US states.
```{r}
library(choroplethr)
data(choroplethr)

head(df_pop_state)
```

When calling `choroplethr` with state level data, `region` must contain state names (e.g. "California" or "CA").

```{r}
state_choropleth(df_pop_state, title="2012 State Population Estimates")
```

choroplethr renders state choropleths of the lower 48 states.  An optional parameter, `showLabels`, determines whether to include state abbreviations in the image.

## County lod

choroplethr comes with a dataset, `df_pop_county`, which contains 2012 population estimates for US counties.
```{r}
head(df_pop_county)
```

When calling `choroplethr` with county level data, `region` must contain [county FIPS codes](http://en.wikipedia.org/wiki/FIPS_county_code).

```{r}
county_choropleth(df_pop_county, title="2012 County Population Estimates")
```

choroplethr renders county maps with an outline of state boundaries.  There are over 3,000 counties in the lower 48 states.  

## ZIP lod

`choroplethr` comes with a dataset, `df_pop_zip`, which contains 2012 population estimates for US [ZIP Code Tabulated Areas (ZCTAs)](https://www.census.gov/geo/reference/zctas.html).  ZCTAs are created and maintained by the US Census Bureau and can be considered approximations of US Postal Codes.

```{r}
head(df_pop_zip)
```

When calling `choroplethr` with ZIP level data, `region` must contain 5 digit ZIP codes.

```{r}
zip_choropleth(df_pop_zip, title="2012 ZIP Code Tabulated Area (ZCTA) Population Estimates")
```

choroplethr renders ZIP level maps as scatterplots.  The longitude and latitude of each ZIP code comes from the [zipcode](http://cran.r-project.org/web/packages/zipcode/index.html) package.  These are technically not choropleth maps because they do not show the boundaries of the ZIP codes.  
