US County Map
===

You can create a choropleth of US Counties with the function `county_choropleth`:

```{r hold=TRUE}
library(choroplethr)

# 2012 US County Population Estimates
data(df_pop_county)
?df_pop_county

?county_choropleth
county_choropleth(df_pop_county)
```

As demonstrated above, the only required parameter to `county_choropleth` is a data.frame.  You can see the optional options by typing ?county_choropleth`.  

# Data Requirements

In order for `state_choropleth` to work, your data must meet certain requirements. Let's take a look at `df_pop_state` more closely.

```{r}
head(df_pop_county)
```

Note that there are two columns: "region" and "value". These two columns are a requirement for all data given to choroplethr. The "value" column can contain be of any type: numeric, factor or string.

There are much more restrictions placed on the "region" column. In particular, entries in the "region" column must **exactly** match how the regions are named in the "region" column of the map data.frame. The county map is named `country.map`:

```{r}

data(country.map)
?country.map

head(country.map)

head(unique(country.map$region))
```


## Formatting your Data

choroplethr provides support for formatting your data with the `country.names` data.frame:

```{r}
data(country.names)
?country.names
head(country.names)
```
