<!--
  %\VignetteEngine{knitr}
%\VignetteIndexEntry{c) US County Choropleths}
-->

US County Chropleths

===

You can create a choropleth of US Counties with the function `county_choropleth`:

```{r hold=TRUE}
library(choroplethr)

?df_pop_county
data(df_pop_county)

?county_choropleth
county_choropleth(df_pop_county)
```

As demonstrated above, the only required parameter to `county_choropleth` is a data.frame.  You can see the optional parameters by typing `?county_choropleth`.  

# Data Requirements

The data.frame that you provide to `county_choropleth` must have one column named "region" and one column named "value". Your entries for "region" must **exactly** match how regions are named in the map which choroplethr uses.  These names are defined in the object `county.names`:

```{r}
library(choroplethrMaps)

?county.names
data(county.names)
head(county.names)
```

In order to use choroplethr, you must use the naming convention in the "region" column of county.names. That is, you must use the numeric version of the county FIPS code - i.e. you must drop any leading zeroes.

# Exploring Data

The `county_choropleth` function provides two parameters to facilitate exploring data: `buckets` and `zoom`.  buckets defaults to 7, which means that there are 7 colors, and an equal number of counties in each color. Valid values for buckets are integers betwen 1 and 7. If buckets is 1 then a continuous scale will be used. zoom defaults to NULL, which means that all counties are shown. You can set it to be a vector of states. You must name your states as defined in the "region" column of `?state.names`.  

As an example, here is how you can use choroplethr to show the population of US Counties on the West Coast.

```{r}
county_choropleth(df_pop_county,
                 title   = "2012 Population Estimates",
                 legend  = "Population",
                 buckets = 1,
                 zoom    = c("california", "washington", "oregon"))
```

# Advanced Options

Any customization outside the optional parameters presented above will require you to create a `CountyChoropleth` object.  choroplethr uses [R6](https://github.com/wch/R6) to take advantage of object-oriented programming.  Here is an example of using the `ggplot2_scale` on the base Choropleth object to customize the palette used.

```{r}
library(ggplot2)

choro = CountyChoropleth$new(df_pop_county)
choro$title = "2012 Population Estimates"
choro$ggplot_scale = scale_fill_brewer(name="Population", palette=2)
choro$render()
```
