US County Map
===

You can create a choropleth of US Counties with the function `county_choropleth`:

```{r hold=TRUE}
library(choroplethr)

# 2012 US County Population Estimates
data(df_pop_county)
?df_pop_county

?county_choropleth
county_choropleth(df_pop_county)
```

As demonstrated above, the only required parameter to `county_choropleth` is a data.frame.  You can see the optional parameters by typing `?county_choropleth`.  

# Data Requirements

In order for `state_choropleth` to work, your data must meet certain requirements. Let's take a look at `df_pop_county` more closely.

```{r}
head(df_pop_county)
```

Note that there are two columns: "region" and "value". These two columns are a requirement for all data given to choroplethr. The "value" column can be of any type: numeric, factor or string.

There are much more restrictions placed on the "region" column. In particular, entries in the "region" column must **exactly** match how the regions are named in the "region" column of the map data.frame. The county map is named `county.map`:

```{r}

data(county.map)
?county.map

head(county.map, 4)

head(unique(county.map$region))
```

choroplethr treats county region names as numeric county FIPS codes. According to the strict definition of county FIPS codes they should be character strings - i.e., leading zeroes should be preserved. However, I have found that the numeric form of county FIPS codes are so widely used, and the conversion from string to numeric so much easier than numeric to string, that I have decided to adopt the numeric convention.

## Formatting your Data

choroplethr provides support for formatting your data with the `county.names` data.frame:

```{r}
data(county.names)
?county.names
head(county.names)
```

If your regions as anything other than numeric county FIPS codes then you can use this data.frame to convert to the format that choroplethr requires.