US County Map
===

You can create a choropleth of US Counties with the function `county_choropleth`:

```{r hold=TRUE}
library(choroplethr)

# 2012 US County Population Estimates
data(df_pop_county)
?df_pop_county

county_choropleth(df_pop_county)
```

As demonstrated above, the only required parameter to `county_choropleth` is a data.frame.  You can see the optional options by typing ?county_choropleth`.  

# Data Requirements

In order for `state_choropleth` to work, your data must meet certain requirements. Let's take a look at `df_pop_state` more closely.

```{r}
head(df_pop_county)
```

Note that there are two columns: "region" and "value". These two columns are a requirement for all data given to choroplethr. In general, choropleths can be viewed as functions which map colors to regions on a map. Your data must reflect this. The "value" column can contain any format of data: numeric, factor or string. 

There are much more restrictions placed on the "region" column. In particular, entries in the "region" column must **exactly** match how the regions are named in the "region" column of the map data.frame. The county map is named `county.map`:

```{r}

data(county.map)
?county.map

head(county.map)

head(unique(county.map$region))
```

Note that all regions are identified by the numeric county FIPS code (I.e. any leading zeros are dropped, and the value is numeric, and not a character string). 

## Formatting your Data

choroplethr provides support for formatting your data with the `county.names` data.frame:

```{r}
data(county.names)
?county.names
head(county.names)
```

If your regions are encoded as state abbreviations, numeric FIPS codes or character FIPS codes, then you can use this table to extract the name that choroplethr requires.