US State Map
===

You can create a choropleth of US States with the function `state_choropleth`:

```{r hold=TRUE}
library(choroplethr)

# 2012 US State Population Estimates
data(df_pop_state)
?df_pop_state

state_choropleth(df_pop_state)
?state_choropleth
```

As demonstrated above, the only requirement to `state_choropleth` is a data.frame that function allows you to set a title, name of the legend, explore various scaling/coloring schemes and zoom in on certain states.  For a full explanation of these options type `?state_choropleth`.  

# Data Requirements

In order for `state_choropleth` to work, your data must meet certain requirements. Let's take a look at `df_pop_state` more closely.

```{r}
head(df_pop_state)
```

Note that there are two columns: "region" and "value". These two columns are requirement for all data given to choroplethr. In general, the "value" column can contain any format of data: numeric, factor or string. 

There are much more restrictions placed on the "region" column. In particular, entries in the "region" column must **exactly** match how the regions are named in the "region" column of the map data.frame.  The state map is named `state.map`:

```{r}

data(state.map)
?state.map

head(state.map)

head(unique(state.map$region))
```

## Formatting your Data

choroplethr provides support for formatting your data with the `state.names` data.frame:

```{r}
data(state.names)
head(state.names)
```

